Active deformation of the Shargyn Basin, a transpressional strike-slip intersection in western Mongolia.

### 2013-05-07 writing/paper/structure.tex
writing.. writing.. writing..
fixing up the maps

\begin{figure}[h!]
  \centering
  \includegraphics[width = 7in, height = 5.0in]{faultmap.png}
  \caption{The black lines are faults with the indicated slip direction and dip direction (for thrusts). The red lines indicate cross-sections and the adjacent letters provide an index for these cross-sections. The white boundaries separate different mapping the areas. The southern area is the mapping performed during this field season, with the smaller enclosed boxes being the areas which we directly observed. The northwestern mapping area of the Sutai Range was performed by \citet{Cunningham2003}. The northeastern mapping was performed by \citet{Dijkstra2006} and as a part of unpublished research by Claire Bucholz.}
  \label{faultmap}
\end{figure}

@@

Further east, along cross-section K-K', we observed a boundary between greenschist grade metasedimentary rocks on the east side and a gneissic unit on the west side. This is interpreted as the furthest northern extent of the southwesternmost of the intersection wedge thrusts. For most of its length, satellite imagery of this fault shows some topographic expression and where observed in the field, it always separates the gneiss and schist from the metasedimentary rocks, indicating that it is an important structural boundary.

>>>>

\begin{figure}[h!]
  \centering
  \includegraphics[width = 7in, height = 5.0in]{faultmap.png}
  \caption{The black lines are faults with the indicated slip direction and dip direction (for thrusts). }
  \label{faultmap}
\end{figure}

@@

Further east, along cross-section K-K', we observed a boundary between greenschist grade metasedimentary rocks on the east side and a gneissic unit on the west side. This is interpreted as the furthest northern extent of the southwestern-most of the intersection wedge thrusts. For most of its length, satellite imagery of this fault shows some topographic expression and where observed in the field, it always separates the gneiss and schist from the metasedimentary rocks, indicating that it is an important structural boundary.

ADD A SECTION ON THE MAIN TRANSECT THROUGH THE WEDGE?!
